### 2018-12-04 tex/paper.tex
Proof for equivalence of conditional gradient and subgradient for dense crf included.

Introducing a temperature parameter $T$ to problem (),

@@

and considering the limit $T \to 0$, problem () becomes

@@

However, using the equivalence of relaxed LP objectives and the Lovasz
extension of submodular extensions in proposition
\ref{proposition:potts_equiv}, we are able to compute $s^*$ in ${\mathcal
O}(NL)$ time. Specifically, we use the algorithm of
Ajanthan et al. \citep{ajanthan2017efficient}, which provides an efficient filtering procedure to compute the subgradient of the LP relaxation objective $E({\bf y})$ of (P-LP).\\
%
\vspace{-0.5cm}
{\proposition Computing the subgradient of $E({\bf y})$ in (P-LP) is equivalent to computing the conditional gradient for the submodular function $F_{Potts}$. \label{proposition:subgrad}} 
\newline(Proof in appendix).
%\begin{proof}
%From lemma \ref{lemma:lovasz_lp}, 
%\begin{align}
%    E({\bf y}) &= f({\bf y})  \nonumber \\
%    {} &=  \max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle.\nonumber
%\end{align}
%
%The subdifferential of $E({\bf y})$ at $\bf y_0$ is the `active' linear function at $\bf y_0$. Hence,
%\begin{align}
%    \partial E({\bf y})|_{\bf y = y_0} &=  \argmax_{{\bf s} \in EP(F)} \langle {\bf y_0}, {\bf s} \rangle
%    \label{eq:subgrad}
%\end{align}
%Equation (\ref{eq:subgrad}) is equivalent to ${\bf s}^*$ computation in line \ref{line:cond_grad} of algorithm \ref{algo:fw_inference}, with ${\bf y_0} = - \nabla g({\bf s}_k)$.
%\end{proof}
%

>>>>

Introducing a temperature parameter $T$ to problem (\ref{eq:hop_upper_bound}),

@@

and considering the limit $T \to 0$, problem (\ref{eq:hop_temp}) becomes

@@

However, using the equivalence of relaxed LP objectives and the Lovasz
extension of submodular extensions in proposition
\ref{proposition:potts_equiv}, we are able to compute $s^*$ in ${\mathcal
O}(NL)$ time. Specifically, we use the algorithm of
Ajanthan et al. \citep{ajanthan2017efficient}, which provides an efficient filtering procedure to compute the subgradient of the LP relaxation objective $E({\bf y})$ of (P-LP).\\
%
\vspace{-0.5cm}
{\proposition Computing the subgradient of $E({\bf y})$ in (P-LP) is equivalent to computing the conditional gradient for the submodular function $F_{Potts}$. \label{proposition:subgrad}} 
\newline(Proof in appendix).
\begin{proof}
  For the Potts model, we derived the worst-case optimal extension $F_{Potts}$ by
  making its Lovasz extension $f({\bf y})$ same as the objective function
    $E({\bf y})$ of the worst-case optimal LP relaxation. Hence, we have
\begin{align}
    E({\bf y}) &= f({\bf y})  \nonumber \\
    {} &=  \max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle.\nonumber
\end{align}

The subdifferential of $E({\bf y})$ at $\bf y_0$ is the `active' linear function at $\bf y_0$. Hence,
\begin{align}
    \partial E({\bf y})|_{\bf y = y_0} &=  \argmax_{{\bf s} \in EP(F)} \langle {\bf y_0}, {\bf s} \rangle
    \label{eq:subgrad}
\end{align}
Equation (\ref{eq:subgrad}) is equivalent to ${\bf s}^*$ computation in line \ref{line:cond_grad} of algorithm \ref{algo:fw_inference}, with ${\bf y_0} = - \nabla g({\bf s}_k)$.
\end{proof}
